\documentclass[10pt, a4paper]{article}

% ── Packages ────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[top=1.4cm, bottom=1.4cm, left=1.8cm, right=1.8cm]{geometry}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tabularx}
\usepackage[activate=false]{microtype}

% ── Colours ─────────────────────────────────────────────────
\definecolor{dark}{HTML}{0a0a0a}
\definecolor{mid}{HTML}{0a0a0a}
\definecolor{muted}{HTML}{0a0a0a}
\definecolor{ruled}{HTML}{0a0a0a}

% ── Base settings ───────────────────────────────────────────
\color{dark}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ── List style ──────────────────────────────────────────────
\setlist[itemize]{
  label={\color{muted}\textendash},
  leftmargin=1.2em,
  topsep=2pt,
  itemsep=1.5pt,
  parsep=0pt
}

% ── Section heading ─────────────────────────────────────────
\newcommand{\rsection}[1]{%
  \vspace{7pt}%
  {\small\scshape\color{muted}#1}%
  \vspace{2pt}\par\noindent%
  {\color{ruled}\rule{\linewidth}{0.4pt}}\par%
  \vspace{2pt}%
}

% ── Project block ───────────────────────────────────────────
% \rproject{Name}{github-slug-or-empty}{Stack line}{bullet list}
\newcommand{\rproject}[4]{%
  \noindent\textbf{#1}\par%
  \ifx&#2&\else
    \vspace{-1pt}%
    {\footnotesize\texttt{github.com/PriyanshS/#2}}\par%
  \fi
  \vspace{-1pt}%
  {\small\texttt{#3}}\par%
  \vspace{1pt}%
  #4%
  \vspace{3pt}%
  \noindent{\color{ruled}\rule{\linewidth}{0.3pt}}\par%
  \vspace{4pt}%
}

% ─────────────────────────────────────────────────────────────
\begin{document}
% ─────────────────────────────────────────────────────────────

%% ══ HEADER ══════════════════════════════════════════════════
{\LARGE\bfseries Priyansh Saxena}
\hfill
{\small\color{muted}Indore, Madhya Pradesh, IN}

\vspace{4pt}
{\color{mid}
  Computer Engineer
  \enspace\textperiodcentered\enspace
  B.Tech, NMIMS STME
  \enspace\textperiodcentered\enspace
  Systems Builder
}

\vspace{4pt}
{\small\color{muted}
  \href{mailto:priyanshsaxena50@gmail.com}{Gmail}
  \quad\textbar\quad
  \href{https://github.com/PriyanshS}{GitHub}
  \quad\textbar\quad
  \href{https://www.linkedin.com/in/priyansh-saxena-027a40317}{LinkedIn}
}

\vspace{5pt}
{\color{ruled}\rule{\linewidth}{0.5pt}}
\vspace{4pt}

%% Pitch / Summary
{\small\color{mid}
Curious computer engineering student building across software, data, AI, hardware,
and interfaces. Projects span local-first intelligence tools, embedded monitoring,
hospital operations software, sustainability digital twins, and quantum-classical
optimisation. Strongest in turning broad ideas into working systems with clear
architecture, reproducible setup, documented tradeoffs, and practical user flows.
}

%% ══ EDUCATION ═══════════════════════════════════════════════
\rsection{Education}

\noindent
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \textbf{SVKM's NMIMS --- School of Technology, Management \& Engineering, Indore}
  & {\small\color{muted}2024 -- 2028} \\
\end{tabularx}
{\small\color{mid}B.Tech, Computer Engineering\quad\textperiodcentered\quad Sem IV\quad\textperiodcentered\quad Current CGPA: 9.08/10}\\
{\footnotesize\color{muted}
  Relevant coursework: Data Structures \& Algorithms, DBMS, OOP via Java,
  Microprocessors \& Computer Organisation, Theoretical Computer Science, Digital Logic Design
}

{\footnotesize\color{muted}
  Academic achievement: Qualified NTSE Stage 1 during high school, 2021
}

%% ══ PROJECTS ════════════════════════════════════════════════
\rsection{Projects}

\rproject{AlphaWindow --- Local-first Financial Intelligence Platform}
  {AlphaWindow}
  {TypeScript | Node.js | Express | PostgreSQL | Ollama | Qwen 2.5 | JWT | RAG | Chrome Extension}
  {\begin{itemize}
    \item Designed a local-first research stack connecting browser capture,
      authenticated Express / TypeScript APIs, local Ollama + Qwen~2.5 inference,
      and PostgreSQL archival with no external LLM dependency.
    \item Built AI enrichment for captured research fragments: category labelling,
      sentiment classification, confidence scoring, and metadata-backed sorting
      for finance, defence, technology, energy, and macro signals.
    \item Implemented a private knowledge workflow with PDF / Markdown ingestion,
      multi-source RAG, JWT-protected sessions, schema exploration, raw SQL access,
      setup automation, and ``Doctor Mode'' diagnostics for portability.
  \end{itemize}}

\rproject{ParyayOS / CampusZero --- Campus Sustainability Digital Twin}
  {paryayos-campuszero}
  {TypeScript | Node.js | Three.js | Python | TimescaleDB | InfluxDB | OpenStreetMap | MQTT}
  {\begin{itemize}
    \item Built a campus sustainability prototype with static CSV ingestion and
      simulated IoT telemetry for power, water, and waste monitoring.
    \item Implemented Three.js + OpenStreetMap digital twin, threshold alerts,
      XP-based progress loop, roadmap tracking, and client-side forecasting
      with seasonal adjustment.
    \item Created a 14-item cost-benefit calculator using Indian hardware pricing,
      payback estimates, and carbon-credit modelling; production roadmap targets
      MQTT + time-series storage. \textit{Technex 2026 submission.}
  \end{itemize}}

\rproject{NityaOS --- Hospital Management System}
  {NityaOS}
  {FastAPI | MySQL | React | Pydantic | JWT | Chen ER}
  {\begin{itemize}
    \item Modelled hospital operations across patients, doctors, nurses,
      departments, medical records, billing, users, and audit logs using
      a normalised MySQL schema with views and triggers.
    \item Built FastAPI backend with structured routers, Pydantic validation,
      SQLAlchemy models, JWT authentication, and documented API endpoints.
    \item Developed React workflows for admin, doctor, and patient roles,
      including dashboard analytics, global search, patient timeline, and
      local Docker / script-based startup.
  \end{itemize}}

\rproject{IoT Library Monitoring System}
  {LIbrary-Monitoring-System}
  {C++ | ESP32 | Arduino | Blynk IoT | Node.js | HTML/CSS | DHT22 | HC-SR04 | MQ-2 | LaTeX}
  {\begin{itemize}
    \item Engineered an ESP32 monitoring system for temperature, humidity,
      noise, air quality, motion, and bidirectional occupancy using DHT22,
      MQ-2, PIR, microphone, and dual HC-SR04 ultrasonic sensors.
    \item Streamed telemetry to Blynk IoT across virtual datastreams and
      implemented actuator logic for LEDs and buzzer alerts based on occupancy
      and air-quality thresholds.
    \item Built a Node.js bridge and browser dashboard for real-time monitoring;
      documented wiring, setup, grading criteria, and system design in a
      \LaTeX{} report with TikZ diagrams.
  \end{itemize}}


\rproject{Quantum-Classical Portfolio Optimizer}
  {Quantum-Classical-Portfolio-Optimization}
  {Python | Qiskit | IBM CPLEX | QAOA | yfinance | pandas | rich | plotext}
  {\begin{itemize}
    \item Built a dual-mode NSE portfolio engine with a classical CPLEX path
      for 10-asset Markowitz optimisation and an experimental QAOA path for
      a reduced quantum subproblem.
    \item Added capital-stratified stock selection, 1-year \texttt{yfinance}
      ingestion, allocation output, ROI summaries, and backtesting against
      individual asset trajectories.
    \item Designed a terminal-first interface using \texttt{rich} and
      \texttt{plotext}, with high-resolution backtest charts exported to PNG.
  \end{itemize}}

%% ══ EXPERIENCE ══════════════════════════════════════════════
\rsection{Experience}

\noindent
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \textbf{Community Service Internship} --- Teaching \& Tutoring
  & {\small\color{muted}21 days, 2024} \\
\end{tabularx}
{\footnotesize\color{muted}
  Voluntarily taught children aged 3--16 across subjects including
  Mathematics, English, Social Studies, and Music.
  Adapted instruction style to wide age and ability ranges;
  managed multi-level classrooms with no formal pedagogical training.
  Reinforced that communication is a technical skill.
}

%% ══ TECHNICAL SKILLS ════════════════════════════════════════
\rsection{Technical Skills}

\noindent
\begin{tabular}{@{}p{3.2cm} p{\dimexpr\linewidth-3.2cm}@{}}
  \textbf{Languages}       & TypeScript, Python, JavaScript, SQL, C++, Java, Bash \\[4pt]
  \textbf{Backend / APIs}  & Express, FastAPI, Node.js, REST, JWT, SQLAlchemy, Pydantic  \\[4pt]
  \textbf{Databases}       & PostgreSQL, MySQL, TimescaleDB, InfluxDB, MongoDB     \\[4pt]
  \textbf{AI / Data}       & Ollama, Qwen, RAG, Qiskit, CPLEX, yfinance, pandas   \\[4pt]
  \textbf{Systems / Tools} & Three.js, Git, Linux, Docker, \LaTeX{}, Vite, Mermaid \\[4pt]
  \textbf{Embedded / IoT}  & ESP32, Arduino, Blynk, C++, MQTT concepts, HC-SR04, DHT22 \\[4pt]
  \textbf{Learning Focus}  & Modern C++, systems programming, Spring MVC, backend architecture
\end{tabular}

%% ══ BEYOND CODE ═════════════════════════════════════════════
\rsection{Beyond Engineering}

{\small\color{mid}
I read extensively in history, political philosophy, and international relations ---
particularly the deep history of the Indian subcontinent, the mechanics of state formation,
and how civilisations handle the transition from oral to written knowledge systems.
Philosophy of mind and epistemology interest me for the same reason
distributed systems do: both are fundamentally about what it means to \textit{know} something,
and how that knowledge degrades across transmission.
Off the screen, I play basketball --- the one domain where latency is truly unforgiving.
}

\end{document}
